### 2021-11-16 ANA-TOPQ-2019-17-PAPER-metadata.tex
minor update
fix spelling

A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and the
Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$. 
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.  
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
%The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
}

@@

% Comment deadline
\AtlasCoverCommentsDeadline{1 November 2021}

>>>>

A search for flavour-changing neutral current $tqH$ interactions with a top quark, an up-type quark ($q=u, c$), and the
Standard Model Higgs boson is presented. The Higgs boson decays to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$. 
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.  
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
%The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
}

@@

% Comment deadline
\AtlasCoverCommentsDeadline{1 January 2022}

### 2021-11-16 sections/conclusion.tex
fix spelling

A search for flavour-changing neutral current $tqH$ interections with a top quark,	an up-type quark ($q=u, c$), and the
Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.

>>>>

A search for flavour-changing neutral current $tqH$ interections with a top quark,	an up-type quark ($q=u, c$), and the
Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.

### 2021-11-16 sections/data_presel.tex
fix spelling

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identificaiton so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

>>>>

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

### 2021-11-16 sections/signal_background_modeling.tex
fix spelling

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates.
%and the jet multiplicity is low.
This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the tight lepton isolation using PLIV, which is widely used in ATLAS physics analyses.

@@

In the $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined preformace (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define the different SRs, except
that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
the ratio of the Data-MC($\mathrm{real~tau}$) yields passing the medium tau ID to which failing the medium tau ID from different control regions and
the differences are treated as part of systematics.

>>>>

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
%and the jet multiplicity is low.
This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the tight lepton isolation using PLIV, which is widely used in ATLAS physics analyses.

@@

In the $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined performance (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define the different SRs, except
that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
The templates are acquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
the ratio of the Data-MC($\mathrm{real~tau}$) yields passing the medium tau ID to which failing the medium tau ID from different control regions and
the differences are treated as part of systematics.

### 2021-11-16 sections/strategy_Htautau.tex
minor update
fix spelling

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
    The description of each variable is provided in the text.}}
\label{tab:importance_xTFW}
\input{\FCNCTables/Importance/xTFW/Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
    The description of each variable is provided in the text.}}
\label{tab:importance_tthML}
\input{\FCNCTables/Importance/tthML/Merged}
\end{table*}
%%%%%%%%%%%%%%%

@@

\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.

>>>>

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel.
    The description of each variable is provided in the text.}}
\label{tab:importance_tthML}
\input{\FCNCTables/Importance/tthML/Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
    The description of each variable is provided in the text.}}
\label{tab:importance_xTFW}
\input{\FCNCTables/Importance/xTFW/Merged}
\end{table*}

%%%%%%%%%%%%%%%

@@

\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant mass of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.

### 2021-11-16 sections/systematic_uncertainties.tex
fix spelling

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertianty is
below 5\% for most jets and below 1\% for central jets with pT between 300 GeV and 2 TeV. The difference between the JER
in data and MC is represented by one NP. It is applied on the MC by smearing the jet pT within the prescribed uncertainty.

@@

A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton show generator, the uncertainty in the value of $\alpha_s$ when modeling intial-state radiation (ISR), the choice of the renormalisation scale when modeling final-state radiation (FSR).
%%An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
%%cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
%%scales, as well as from the top-quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
%%to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
%%with the NNPDF3.0(NLO), CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3(LO) 5F FFN~\cite{Ball:2012cx} PDF sets.

@@

Another significancant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
considered for these samples: the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty,
variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal)
with MMHT2014nnlo68cl and CT14nnlo PDF sets.

@@

%A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation. A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement. Therefore, a overall sytematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.

>>>>

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
below 5\% for most jets and below 1\% for central jets with pT between 300 GeV and 2 TeV. The difference between the JER
in data and MC is represented by one NP. It is applied on the MC by smearing the jet pT within the prescribed uncertainty.

@@

A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton show generator, the uncertainty in the value of $\alpha_s$ when modeling initial-state radiation (ISR), the choice of the renormalisation scale when modeling final-state radiation (FSR).
%%An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
%%cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
%%scales, as well as from the top-quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
%%to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
%%with the NNPDF3.0(NLO), CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3(LO) 5F FFN~\cite{Ball:2012cx} PDF sets.

@@

Another significant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty,
variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
with MMHT2014nnlo68cl and CT14nnlo PDF sets.

@@

%A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation. A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement. Therefore, a overall systematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.
